\documentclass[aspectratio=169]{beamer}
\input{shared/tgir-beamer-preamble}

\title{End User Slides}
\subtitle{\product}
\author{TG Investments and Research}
\date{\docdate}

\begin{document}
\frame{\titlepage}

\begin{frame}{What Users Need To Know}
\begin{itemize}
    \item Login at \code{http://127.0.0.1:5050}.
    \item Main workflow lives on \code{/dashboard}.
    \item Five trades are always visible on the blotter.
    \item The top bar keeps nav, research, GitHub, export, realtime, and reset controls together.
    \item Detailed trade changes happen in the dedicated editor pages.
\end{itemize}
\end{frame}

\begin{frame}{Dashboard Components}
\begin{itemize}
    \item Valuation date field shared by all rates analytics.
    \item SOFR curve inputs plus a compact market-rate / zero-rate table.
    \item Market-versus-zero-rate chart plus mean reversion shown as a percentage.
    \item Workbook ATM swaption normal-vol matrix.
    \item Bermudan pricing grid.
    \item On-demand forward-strip and OIS-repricing diagnostics.
    \item SPX cliquet market assumptions.
\end{itemize}
\end{frame}

\begin{frame}{Trade Editors}
\begin{itemize}
    \item Swap: direction, notional, fixed coupon, tenor.
    \item European swaption: strike, expiry, underlying tenor, then Hull-White 1F + Jamshidian pricing.
    \item The four rates trades start at \code{100,000,000.00} notionals by default.
    \item Bermudan swaption editors: first exercise, fixed final maturity, pay/reset frequency, model choice.
    \item Bermudan detail view shows the exercise-to-swap mapping, helper source points, and Hull-White versus G2++ comparison.
    \item Equity cliquet: option type, quantity, moneyness, maturity, reset frequency.
\end{itemize}
\end{frame}

\begin{frame}{Cliquet Page Outputs}
\begin{itemize}
    \item Analytic Greeks from QuantLib.
    \item Reset-by-reset forward-start decomposition.
    \item Spot-volatility scenario matrix.
    \item Monte Carlo payoff distribution summary.
\end{itemize}
\end{frame}

\begin{frame}{Exports And Reference Pages}
\begin{itemize}
    \item Download \code{/curve-debug.csv} for audit or spreadsheet work.
    \item Use \code{/quantlib-data-model} for the full model map.
    \item The model page also lists the swaption and cliquet research papers.
\end{itemize}
\end{frame}

\begin{frame}{Troubleshooting}
\begin{itemize}
    \item Login issues usually mean the local \code{.env} credentials are wrong.
    \item Bermudan risk is slow because the model recalibrates on each relevant bump.
    \item Cliquet rendering is slower than the other trades because it includes scenarios and Monte Carlo analytics.
    \item Use the reset button to restore the demo state.
\end{itemize}
\end{frame}

\end{document}
