\documentclass[11pt]{article}
\input{shared/tgir-article-preamble}

\title{Testing And Regression Guide\\\large \product}
\author{TG Investments and Research}
\date{\docdate}

\begin{document}
\maketitle
\tableofcontents
\newpage

\section{Purpose}
This document describes the test suite in detail and defines the regression-testing approach for future changes.

\section{Test Inventory}
\begin{longtable}{p{0.28\textwidth}p{0.22\textwidth}p{0.42\textwidth}}
\toprule
File & Type & Coverage \\
\midrule
\path{tests/test_smoke.py} & Route and integration smoke tests & Login flow, protected routes, dashboard rendering, editor rendering, model page rendering, CSV download, and market/trade update round-trips. \\
\path{tests/test_sofr_curve.py} & Quantitative calibration tests & OIS curve repricing, zero-rate and forward-strip checks, Bermudan helper repricing, workbook-reference Bermudan price checks, matrix shape checks, and risk-ladder sanity checks. \\
\path{tests/test_cliquet.py} & Structured-product identity tests & Ten cliquet reductions to simpler or deterministic cases with known answers. \\
\bottomrule
\end{longtable}

\section{Current Release Gates}
The current minimum release gate is:
\begin{lstlisting}
./.venv/bin/python -m unittest tests.test_cliquet
./.venv/bin/python -m unittest tests.test_sofr_curve
./.venv/bin/python -m unittest tests.test_smoke
\end{lstlisting}

\section{Calibration Tests}
\subsection{SOFR Curve Repricing}
The curve regression test rebuilds the quoted OIS strip against the bootstrapped curve and asserts near-zero NPVs. This catches:
\begin{itemize}[leftmargin=1.5em]
    \item accidental helper changes,
    \item day-count or calendar regressions,
    \item broken quote normalization, and
    \item curve interpolation changes.
\end{itemize}

\subsection{Bermudan Helper Repricing}
The Bermudan calibration test verifies that every \code{ql.SwaptionHelper} implied by the trade's fixed-maturity call schedule remains numerically well aligned after short-rate calibration. This is critical because a Bermudan mark can remain numerically plausible even when the calibration strip is visibly wrong. Separate schedule tests confirm that fixed-maturity Bermudans shorten the remaining underlying tenor as exercise dates roll forward, that interpolated expiries retain the correct matrix source points, and that the alternate G2++ path still builds the expected parameter set.

\section{Cliquet Identity Portfolio}
The cliquet regression suite does not rely on arbitrary golden numbers. Instead it uses structural identities:
\begin{enumerate}[leftmargin=1.5em]
    \item single-period ATM call equals a vanilla call,
    \item single-period ATM put equals a vanilla put,
    \item single-period OTM call equals the matching vanilla call,
    \item single-period ITM put equals the matching vanilla put,
    \item two-period call equals the sum of two forward-start calls,
    \item two-period put equals the sum of two forward-start puts,
    \item four equal-quarter calls collapse to four identical quarter calls when the setup is stationary,
    \item four equal-quarter puts collapse to four identical quarter puts when the setup is stationary,
    \item zero-volatility call strip reduces to discounted deterministic intrinsic values, and
    \item zero-volatility put strip reduces to discounted deterministic intrinsic values.
\end{enumerate}

\section{Regression Strategy}
\subsection{Principles}
\begin{itemize}[leftmargin=1.5em]
    \item Prefer invariant-based tests over snapshot-style fixed numbers.
    \item Reprice calibration instruments directly wherever a model is calibrated.
    \item Keep route tests separate from core pricing tests so failures are easier to localize.
    \item Use deterministic seeds when Monte Carlo is involved.
\end{itemize}

\subsection{When To Add A New Regression Test}
Add a regression test when:
\begin{itemize}[leftmargin=1.5em]
    \item a bug was fixed,
    \item a new instrument or market input was added,
    \item a pricing identity can be stated cleanly,
    \item a calibration path changed, or
    \item a UI route gained material analytical content.
\end{itemize}

\section{Performance And Runtime}
The suite contains intentionally heavy tests:
\begin{itemize}[leftmargin=1.5em]
    \item Bermudan calibration repricing is computationally expensive.
    \item The cliquet editor smoke test is slower than typical page renders because it runs scenario and Monte Carlo analytics.
\end{itemize}
These tests are still kept in the standard suite because the repo is a quantitative sandbox and correctness matters more than ultra-short CI runtimes.

\section{Recommended Future Extensions}
\begin{itemize}[leftmargin=1.5em]
    \item add a deterministic reference test for the cliquet Monte Carlo summary path,
    \item add page-load budget checks if UI latency becomes a concern,
    \item add environment-parity smoke checks for the production WSGI entrypoint, and
    \item add deploy-time smoke checks against a real production health endpoint.
\end{itemize}

\section{Failure Triage}
If a regression appears:
\begin{enumerate}[leftmargin=1.5em]
    \item identify whether the failing layer is route, calibration, or payoff identity,
    \item rerun the smallest targeted test file first,
    \item compare normalized input state before comparing outputs,
    \item verify calendar and day-count assumptions, and
    \item only then inspect numerical tolerances.
\end{enumerate}

\end{document}
